Global patterns of forest autotrophic carbon fluxes

### 2019-11-14 manuscript/manuscript draft.Rmd
knit manuscript
(after fixing special character problem)
added Helene's review files

---
title: "Global patterns of forest autotrophic carbon fluxes"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene Muller-Landau, Kristina J. Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}

@@

**Forests' autotrophic carbon flux (FACF, bbl:define) influences all organic matter stocks in ecosystems and is linked to cycling of energy, water, and nutrients** (**REFS; *Piao et al. 2010. Forest annual carbon cost: a global‐scale analysis of autotrophic respiration. Ecology 91(3), 652-661Ƴ* **). Forest productivity sets the energy ultimately available to heterotrophic organisms (including microbes), in turn influencing their abundance (**REFS**) and possibly diversity ([Waide et al. 2009](https://www.annualreviews.org/doi/abs/10.1146/annurev.ecolsys.30.1.257)**REFS**)--but probably not individual metabolic rate (**Anderson & Jetz 2005, but check more recent literature**). However, our ability to draw general macroscopic conclusions regarding global variation in multiple productivity variables with respect to climate has been limited in that these analyses often mix forests that vary in stand age, disturbance history, and/or management status; do not always sufficiently parse related variables (*e.g.*, combining net primary productivity records with and without belowground components); and typically consider only one or a few variables at a time.

>>>>

---
title: "Global patterns of forest autotrophic carbon fluxes"
author: "Rebecca Banbury Morgan, Valentine Herrmann, Norbert Kunert, Ben Bond-Lamberty, Helene C. Muller-Landau, Kristina J. Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [library.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}

@@

**Forests' autotrophic carbon flux (FACF, bbl:define) influences all organic matter stocks in ecosystems and is linked to cycling of energy, water, and nutrients** (**REFS; *Piao et al. 2010. Forest annual carbon cost: a global‐scale analysis of autotrophic respiration. Ecology 91(3), 652-661* **). Forest productivity sets the energy ultimately available to heterotrophic organisms (including microbes), in turn influencing their abundance (**REFS**) and possibly diversity ([Waide et al. 2009](https://www.annualreviews.org/doi/abs/10.1146/annurev.ecolsys.30.1.257)**REFS**)--but probably not individual metabolic rate (**Anderson & Jetz 2005, but check more recent literature**). However, our ability to draw general macroscopic conclusions regarding global variation in multiple productivity variables with respect to climate has been limited in that these analyses often mix forests that vary in stand age, disturbance history, and/or management status; do not always sufficiently parse related variables (*e.g.*, combining net primary productivity records with and without belowground components); and typically consider only one or a few variables at a time.
